Measuring contrast processing in the visual system using SSVEP

### 2024-05-05 review.qmd
References update

Electrophysiological and psychophysical measurements of the effect of attention on both luminance and chromatic contrast have strongly implicated gain control as an underlying mechanism [@DiRusso1999; @DiRusso2001; @Lu1998]. These effects also appear to differ between chromatic and achromatic pathways [@DiRusso1999b] - perhaps as a result of the different levels of nonlinear gain control in the early precotical magno,  parvo and konio-cellular pathways [DerringtonLennie84, KaplanShapley86, LeePokornyJOSA90, SolomonLennie2005].  In the late 2000s a comprehensive theoretical model for attentional modulation was developed that framed it as a gain control computation [@Reynolds2009; @Boynton2009]. This framework has proven to be influential - explaining a wide range of phenomena from the earlier literature and demonstrating subtle interactions between the size of the attentional 'spotlight' and the stimulus configuration which rationalise many apparent contradictions in the literature. Direct measurements of attentional modulation of achromatic SSVEP signals are broadly consistent with this model [@Lauritzen2010, @Hou2016, @Martinovic2018] and confirm the relatively weaker role of spatial attention on responses driven by chromatic stimuli - particularly those that isolate the opponent S-(L+M) cone pathway [@Wang2011, @Highsmith2010]. The gain control model of attention can also be extended to SSVEP studies of feature-based attention which show that the modulatory effects can be targeted to the most informative neuronal populations [@Verghese2012].

@@

Probably a summary of BCIs here.

>>>>

Electrophysiological and psychophysical measurements of the effect of attention on both luminance and chromatic contrast have strongly implicated gain control as an underlying mechanism [@DiRusso1999; @DiRusso2001; @Lu1998]. These effects also appear to differ between chromatic and achromatic pathways [@DiRusso1999b] - perhaps as a result of the different levels of nonlinear gain control in the early pre-cortical magno-, parvo- and konio-cellular pathways [@Derrington1984b; @Kaplan1986; @Lee1990; @Solomon2005]. In the late 2000s a comprehensive theoretical model for attentional modulation was developed that framed it as a gain control computation [@Reynolds2009; @Boynton2009]. This framework has proven to be influential - explaining a wide range of phenomena from the earlier literature and demonstrating subtle interactions between the size of the attentional 'spotlight' and the stimulus configuration which rationalise many apparent contradictions in the literature. Direct measurements of attentional modulation of achromatic SSVEP signals are broadly consistent with this model [@Lauritzen2010, @Hou2016, @Martinovic2018] and confirm the relatively weaker role of spatial attention on responses driven by chromatic stimuli - particularly those that isolate the opponent S-(L+M) cone pathway [@Wang2011, @Highsmith2010]. The gain control model of attention can also be extended to SSVEP studies of feature-based attention which show that the modulatory effects can be targeted to the most informative neuronal populations [@Verghese2012].

@@

Probably a summary of BCIs here @Zhu2010
